---
title: "Anonymising a full folder"
date: "v1, December 7, 2017"
output: md_document
---

# Goal: anonymise a full folder in one single line

The simple function **ano()** will anonymise specified columns in a directory, using the [SHA-2](https://en.wikipedia.org/wiki/SHA-2) algorithm. The SHA-2 is a deterministic hash funciton. This is used because same key might appear in several files, preventing from using simple stochastic keys. As such, original names could be found by brute force. Using sha256, one needs 2^32 = 4 billions, while for 
sha512, it is 2^64 = 1.8 e+19.

The funciton does:

 1. Read all files with a given extension (**extension** = csv or dta)
 2. Search for the coumns indicated by user (argument **cols_id**)
 3. Use R [digest::digest](https://www.rdocumentation.org/packages/digest/versions/0.6.12/topics/digest) function, with **algo**= *sha256*.
 4. Write the files. Either in a newly created  folder adding *_ANONYMISED*, or simply overwrite the files in original folder (**overwrite**=TRUE)

Simply use the function:

```{r, eval=FALSE}
source("https://raw.githubusercontent.com/MatthieuStigler/anonymize_folder/master/anonymize_main.R")
ano(dir, cols_id = c("pers", "address"))
```



## Example 

### Load the function
```{r, message=FALSE}
source("https://raw.githubusercontent.com/MatthieuStigler/anonymize_folder/master/anonymize_main.R")
```


### Create fake dataset

```{r}
library(tidyverse)
names <- c("Bob", "John", "Harry")
address <- c("House Street", "Main Street", "Central Av.")
file_1 <- data_frame(pers = names, address=address, data=rnorm(3))
file_2 <- data_frame(person = rep(names,each=2), data=sample(letters, size=6),
                     income=rnorm(6))
```

Check them:

```{r}
file_1
file_2
```

Write this dataset on your disk:

```{r}
temp_dir <- tempdir()
path_1 <- paste(temp_dir, "file_1.csv", sep="/")
path_2 <- paste(temp_dir, "file_2.csv", sep="/")
write_csv(file_1, path_1)
write_csv(file_2, path_2)
```

## test the function

Here the cols are pers, person, address and income. We specify the argument **trim**=12 just for seeing the output:
```{r}
ano(dir=temp_dir, cols_id = c("pers", "address", "person", "income"), trim=12)
```

Files have been written. Read now:

```{r}
read_csv(paste(temp_dir, "_ANONYMISED/file_1.csv", sep=""))
read_csv(paste(temp_dir, "_ANONYMISED/file_2.csv", sep=""))
```

