---
title: "Anonymising a full folder"
date: "v1, December 7, 2017"
output: md_document
---

# Goal: anonymise a full folder in one single line

The simple function **ano()** will anonymise specified columns in a directory, using the *sha256* algorithm. It does:

 1. Read all files with a given extension (**extension** = csv or dta)
 2. Search for the coumns indicated by user (argument **cols_id**)
 3. Use R digest::digest function, with algorithm *sha256*. NOTE: digest syays *Please note that this package is not meant to be used for cryptographic purposes *
 4. Write the files. Either overwrite, or write adding *ANO* in name

Simply use the function:

```{r, eval=FALSE}
source("https://raw.githubusercontent.com/MatthieuStigler/anonymize_folder/master/anonymize_main.R")
ano(dir, cols_id = c("pers", "address"))
```



## Example 

### Load the function
```{r, message=FALSE}
source("https://raw.githubusercontent.com/MatthieuStigler/anonymize_folder/master/anonymize_main.R")
```


### Create fake dataset

```{r}
library(tidyverse)
names <- c("Bob", "John", "Harry")
address <- c("House Street", "Main Street", "Central Av.")
file_1 <- data_frame(pers = names, address=address, data=rnorm(3))
file_2 <- data_frame(person = rep(names,each=2), data=sample(letters, size=6),
                     income=rnorm(6))
```

Check them:

```{r}
file_1
file_2
```

Write this dataset on your disk:

```{r}
temp_dir <- tempdir()
path_1 <- paste(temp_dir, "file_1.csv", sep="/")
path_2 <- paste(temp_dir, "file_2.csv", sep="/")
write_csv(file_1, path_1)
write_csv(file_2, path_2)
```

## test the function

Here the cols are pers, person, address and income. We specify the argument **trim**=12 just for seeing the output:
```{r}
ano(dir=temp_dir, cols_id = c("pers", "address", "person", "income"), trim=12)
```

Files have been written. Read now:

```{r}
read_csv(path_1)
read_csv(path_2)
```

